Prediction of US election with linear model

### 2024-10-21 paper/paper.qmd
add literature review to introduction

This paper fills the gap by building a hybrid election forecasting model following the strategies mentioned by @pasek. We incorporate aggregation by filtering the polls by numeric grade that indicates pollster’s reliability, prediction that incorporates historical data and economic indicators, and hybrid approaches that leverages Bayesian techniques, allowing for a dynamic prediction of the U.S. presidential election.

>>>>

This paper fills the gap by building a hybrid election forecasting model following the strategies mentioned by @pasek. As @pasek described in their article, aggregation involves determining which surveys are worth including, as well as selecting, combining and averaging results from multiple polls to reduce individual biases and errors. Prediction modeling adds other data to the model that predicts election outcomes based on current dynamics. Hybrid models like the Bayesian approach incorporates prior beliefs based on historical data or expert knowledge and new evidence like economic updates to dynamically adjust the forecast as the campaign progresses. We incorporate aggregation by filtering the polls by numeric grade that indicates pollster’s reliability, prediction that incorporates historical data and economic indicators, and hybrid approaches that leverages Bayesian techniques, allowing for a dynamic prediction of the U.S. presidential election.
